Tutorial_4

### 2024-12-13 Tutorial_4.Rmd
update 3a 3b 4.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

# plot
p4.1 <- ggplot(tidy_fixed, aes(x = bin, y = value, fill=prime)) +  
  stat_halfeye(alpha=0.7) +
  labs(title = "Model bi cloglog",
       x = "time bin", y = "cloglog") +
  scale_fill_brewer(palette = "Dark2") 
p4.1

ggsave ("Tutorial_4_planning/figures/index_cloglog.jpeg",
        width = 6, height = 4, dpi = 800)
```

@@

```{r plot-bi-hazards}
p4.2 <- ggplot(tidy_haz, aes(x = bin, y = hazard,
                                    fill=prime)) +  
  stat_halfeye(alpha=0.7) +
  labs(title = "hazard estimates",
       x = "time bin", y = "hazard") +
  scale_fill_brewer(palette = "Dark2") +
  scale_y_continuous(limits = c(0,1), breaks = seq(0,1,0.25)) 
p4.2

ggsave ("Tutorial_4_planning/figures/index_hazard.jpeg",
        width = 6, height = 4, dpi = 800)
```

@@

```{r plot-raw-plus-d1}
p5.4 <- (p3.1 / p5.3) +
   plot_layout(guides = 'collect',
               axes = 'collect')
p5.4

ggsave ("Tutorial_4_planning/figures/raw_vs_d1.jpeg",
        width = 8, height = 8, dpi=800)
```

@@

```{r load-sim1}
sx1 <- read_csv("Tutorial_4_planning/data/sim1/sim1_data.csv") %>%
  mutate(exp=factor(exp),
         subj_n=factor(subj_n),
         rep_n=factor(rep_n),
         b6c = factor(b6c,
                      levels = c("-1.94", "-1.5", "-0.67"),
                      labels = c("25%", "50%", "75%")),
         subj=factor(subj),
         bin=factor(bin))
sx1
```

@@

```{r exp-summary-sim1}
sx1_exp <- sx1 %>% 
  group_by(exp, subj_n, rep_n, b6c, condition, bin) %>% 
  summarise(exp_mean_outcome = mean(mean_outcome, na.rm = TRUE),
            exp_mean_sum=mean(sum, na.rm = TRUE),
            exp_sum=sum(sum),
            n = length(unique(subj)), 
            sd=sd(mean_outcome, na.rm = TRUE),
            sem = (sd/sqrt(length(unique(subj)))),
            .groups = "drop")
sx1_exp
```

@@

```{r sim-summary-sim1}
sx1_sim <- sx1_exp %>% 
  group_by(subj_n, rep_n, b6c, condition, bin) %>% 
  summarise(sim_mean_outcome = mean(exp_mean_outcome, na.rm = TRUE),
            sim_mean_sum = mean(exp_mean_sum, na.rm = TRUE),
            sim_sum = mean(exp_sum, na.rm = TRUE),
            n = length(unique(exp)), 
            sd=sd(exp_mean_outcome, na.rm = TRUE),
            sem = (sd/sqrt(length(unique(exp)))),
            .groups = "drop")
sx1_sim
```

@@

```{r sim1-violin}
p9.1 <- ggplot(sx1_sim, 
                aes(x = bin, y = sim_mean_outcome, 
                    colour = condition)) +
  geom_jitter(data=sx1_exp, aes(y = exp_mean_outcome),
              alpha=0.5, width = 0.1, height = 0) +
  geom_line(aes(group = condition)) + 
  geom_point(size=2, colour = "black") +
  geom_errorbar(aes(ymin = sim_mean_outcome-sem*1.96, ymax = sim_mean_outcome+sem*1.96),
                width=.2, colour = "black") +
  scale_colour_brewer(palette = "Dark2") +
  scale_y_continuous(limits = c(0,1), breaks = seq(0,1,0.25)) +
  labs(x="time bin",
       y="outcome") + 
  facet_grid(fct_rev(rep_n)~b6c)
p9.1

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=F)
```

@@

# plot
p4.1 <- ggplot(tidy_fixed, aes(x = bin, y = value, fill=prime)) +  
  stat_halfeye(alpha=0.7) +
  labs(title = "Model bi cloglog",
       x = "time bin", y = "cloglog") +
  scale_fill_brewer(palette = "Dark2") 
p4.1
```

```{r eval=F}
ggsave ("Tutorial_4_planning/figures/index_cloglog.jpeg",
        width = 6, height = 4, dpi = 800)
```

@@

```{r plot-bi-hazards}
p4.2 <- ggplot(tidy_haz, aes(x = bin, y = hazard,
                                    fill=prime)) +  
  stat_halfeye(alpha=0.7) +
  labs(title = "hazard estimates",
       x = "time bin", y = "hazard") +
  scale_fill_brewer(palette = "Dark2") +
  scale_y_continuous(limits = c(0,1), breaks = seq(0,1,0.25)) 
p4.2
```

```{r eval=F}
ggsave ("Tutorial_4_planning/figures/index_hazard.jpeg",
        width = 6, height = 4, dpi = 800)
```

@@

```{r plot-raw-plus-d1}
p5.4 <- (p3.1 / p5.3) +
   plot_layout(guides = 'collect',
               axes = 'collect')
p5.4
```

```{r eval=F}
ggsave ("Tutorial_4_planning/figures/raw_vs_d1.jpeg",
        width = 8, height = 8, dpi=800)
```

@@

```{r load-sim1, eval=F}
sx1 <- read_csv("Tutorial_4_planning/data/sim1/sim1_data.csv") %>%
  mutate(exp=factor(exp),
         subj_n=factor(subj_n),
         rep_n=factor(rep_n),
         b6c = factor(b6c,
                      levels = c("-1.94", "-1.5", "-0.67"),
                      labels = c("25%", "50%", "75%")),
         subj=factor(subj),
         bin=factor(bin))
sx1
```

@@

```{r exp-summary-sim1, eval=F}
sx1_exp <- sx1 %>% 
  group_by(exp, subj_n, rep_n, b6c, condition, bin) %>% 
  summarise(exp_mean_outcome = mean(mean_outcome, na.rm = TRUE),
            exp_mean_sum=mean(sum, na.rm = TRUE),
            exp_sum=sum(sum),
            n = length(unique(subj)), 
            sd=sd(mean_outcome, na.rm = TRUE),
            sem = (sd/sqrt(length(unique(subj)))),
            .groups = "drop")
sx1_exp
```

@@

```{r sim-summary-sim1, eval=F}
sx1_sim <- sx1_exp %>% 
  group_by(subj_n, rep_n, b6c, condition, bin) %>% 
  summarise(sim_mean_outcome = mean(exp_mean_outcome, na.rm = TRUE),
            sim_mean_sum = mean(exp_mean_sum, na.rm = TRUE),
            sim_sum = mean(exp_sum, na.rm = TRUE),
            n = length(unique(exp)), 
            sd=sd(exp_mean_outcome, na.rm = TRUE),
            sem = (sd/sqrt(length(unique(exp)))),
            .groups = "drop")
sx1_sim
```

@@

```{r sim1-violin, eval=F}
p9.1 <- ggplot(sx1_sim, 
                aes(x = bin, y = sim_mean_outcome, 
                    colour = condition)) +
  geom_jitter(data=sx1_exp, aes(y = exp_mean_outcome),
              alpha=0.5, width = 0.1, height = 0) +
  geom_line(aes(group = condition)) + 
  geom_point(size=2, colour = "black") +
  geom_errorbar(aes(ymin = sim_mean_outcome-sem*1.96, ymax = sim_mean_outcome+sem*1.96),
                width=.2, colour = "black") +
  scale_colour_brewer(palette = "Dark2") +
  scale_y_continuous(limits = c(0,1), breaks = seq(0,1,0.25)) +
  labs(x="time bin",
       y="outcome") + 
  facet_grid(fct_rev(rep_n)~b6c)
p9.1
